Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Sec 3.2

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback, 
as implemented on modern FPGAs or ICs. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop digitalized dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behaviour \cite{astrom1997computer}. 
As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature. 
Further, we will encompass the digital nature of the controller, which manipulates quantities with finite precision.

@@

Our algorithm to select suitable FWL word widths to model plant behaviour employs a heuristic based on user-provided controller word-width specifications. For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis. This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.

>>>>

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback control algorithm, 
as implemented on modern FPGAs or DSPs. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a state feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop discrete dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behavior \cite{astrom1997computer}. 
As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature. 
Further, we will encompass the digital nature of the controller, which manipulates quantities with finite precision.

@@

Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications. For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis. This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.
